Watch Out for the Bully! Job Interference Study on Dragonfly Network

### 2016-04-11 background.tex
trivial tweak

\textbf{Progressive Adaptive:} As opposed to adaptive routing, the decision to adaptively route message packets is continually re-evaluated within the source group until a non-minimal route is chosen; the re-evaluation does not occur in intermediate groups~\cite{jiang}.
Progressive adaptive routing is capable of handling scenarios where the minimal route is congested but the source router has not been informed yet.

>>>>

\textbf{Progressive Adaptive:} As opposed to adaptive routing, the decision to adaptively route a packet is continually re-evaluated within the source group until a non-minimal route is chosen; the re-evaluation does not occur in intermediate groups~\cite{jiang}.
Progressive adaptive routing is capable of handling scenarios where the minimal route is congested but the source router has not been informed yet.

### 2016-04-11 study_workload_1.tex
trivial tweak

The study of Workload~\Rmnum{1} consists of two parts. First, we analyze the overall network performance when Workload~\Rmnum{1} is running under different placement and routing configurations. Second, we isolate each application from the workload and analyze its performance both on a per-rank basis as well as by considering router traffic resident to application ranks. The analysis allows us to identify the ``bully'' in Workload~\Rmnum{1}.

>>>>

The study of Workload~\Rmnum{1} consists of two parts. First, we analyze the overall network performance when Workload~\Rmnum{1} is running under different placement and routing configurations. Second, we isolate each application from the workload and analyze its performance on both a per-rank basis as well as by considering router traffic resident to application ranks. The analysis allows us to identify the ``bully'' in Workload~\Rmnum{1}.
